### 2020-01-21 docs/ANE2020/contents.tex
rename the PHYSOR2020 folder to agree with the new publication goal
Results of homogeneous case
Added results to ANE-2020 tex file.

@@

xy

% ------------------------------------------
\section{Conclusions}
\label{sec:conc}

>>>>

It can be noted that the signs before the correction terms are arbitrary, with no need to follow a specific physical meaning. 

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_I400_RMitr250.pdf}
	\caption{Comparison of the fluxes as calculated by the reference S$_N$, RM-CMFD, RM-pCMFD codes, and a standard multigroup diffusion without RM correction ($D_0$). The insets show a zoom-in of the fluxes near the boundary. Results shown here after 250 Ronen iterations and 400 cells.}
	\label{fig:slab-fluxes}		
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($\delta D^+, \delta D^-$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
	\label{fig:slab-RM-corr-factor}
\end{figure}

\begin{figure}[htbp]
	% convergence
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_k_over_I400_RMitr250.pdf}	
	\caption{Convergence of the criticality eigenvalue along 250 Ronen iterations.}
	\label{fig:conv}
\end{figure}

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_I400_RMitr250.pdf}
	\caption{The spatial flux deviation of the RM-CMFD and RM-pCMFD iterations with respect to the reference S$_{16}$ solution for the left half slab.}
	\label{fig:conv3}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
	\label{fig:slab-fluxes-dev}
\end{figure}
% ------------------------------------------
\section{Conclusions}
\label{sec:conc}
